Rubin Observatory Scheduling Algorithm and Simulations

### 2022-07-27 ms.tex
ddf table

XXX--table of DDF positions currently used.

@@

\software{Astropy \citep{astropy2013, astropy2018}, 
          Healpy and HEALpix\footnote{\url{http://healpix.sourceforge.net}} \citep{healpix2005, Zonca2019},
          Numpy \citep{harris2020array},
          Matplotlib \citep{Hunter:2007},
          Scipy \citep{2020SciPy-NMeth},
          Pandas \citep{jeff_reback_2022_6702671},
          Scikit-learn \citep{scikit-learn},
          OpenOrb \citep{Granvik2009}}

>>>>

\begin{table}
    \centering
        \begin{tabular}{lcc}
        \toprule
        Short Name &      RA (deg) &     Dec (deg) \\
        \hline
           ELAISS1 &   9.450 & -44.000 \\
           XMM\_LSS &  35.708 &  -4.750 \\
             ECDFS &  53.125 & -28.100 \\
            COSMOS & 150.100 &   2.182 \\
            EDFS\_a &  58.900 & -49.315 \\
            EDFS\_b &  63.600 & -47.600 \\
        \hline
        \end{tabular}
    \caption{Adopted locations for Deep Drilling Fields.}
    \label{tab:ddf_loc}
\end{table}

@@

\software{Astropy \citep{astropy2013, astropy2018}, 
          Healpy and HEALpix\footnote{\url{http://healpix.sourceforge.net}} \citep{healpix2005, Zonca2019},
          Numpy \citep{harris2020array},
          Matplotlib \citep{Hunter:2007},
          Scipy \citep{2020SciPy-NMeth},
          Pandas \citep{reback2022},
          Scikit-learn \citep{scikit-learn},
          OpenOrb \citep{Granvik2009}}
